### 2016-07-08 appendix.tex
Structural changes: Moving HTTP to the Appendix and some editing
Mounting DEVp3 on mnt question

The HTTP description

@@

\begin{lstlisting}[]
# lsblsk
  NAME   MAJ:MIN RM   SIZE RO TYPE MOUNTPOINT
  sda      8:0    0 238.5G  0 disk
    sda1   8:1    0   512M  0 part /boot
    sda2   8:2    0   168G  0 part /
    sda3   8:3    0     2G  0 part [SWAP]
    sda4   8:4    0    68G  0 part
  loop1    7:1    0    67M  0 loop
  loop2    7:2    0   2.2G  0 loop
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

\input{testbed_http}

@@

\begin{lstlisting}[]
# lsblsk
NAME   MAJ:MIN RM   SIZE RO TYPE MOUNTPOINT
...
loop1    7:1    0    67M  0 loop
loop2    7:2    0   2.2G  0 loop
...
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

### 2016-07-08 overlay_fs.tex
Making new partition and detecting and small typographic error when copying
Mounting DEVp3 on mnt question

\begin{lstlisting}[]
# mount ${DEV}p2 ${ROOTDIR}
# sudo sh -c "echo '/dev/mmcblk0p3 /home ext4 defaults,noatime 0 2' >> ${ROOTDIR}/etc/fstab"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

The home folder was originally located in the root filesystem. We should
therefore copy the content to the new home partition:
\begin{lstlisting}[]
# mount ${DEV}p3 ${ROOTDIR}/mnt
# mv ${ROOTDIR}/home/* ${ROOTDIR}/mnt/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

If the steps have been properly made up to this point, the customized image
is ready to be deployed into the \ac{Raspi}s. In the following section, we
indicate how to proceed with the writing of the image into various memory
cards, although a more complex setup with a \ac{HTTP} server is also presented
in Section~\ref{sec:http} of the Appendix.

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card. Insert
a memory card in your machine. It will be available as \texttt{/dev/mmcblkX}
or \texttt{/dev/sdX}.

%In most systems, this memory card was available under \texttt{/dev/mmcblk0}, but this may be
%different on different machines. For internal memory card readers, it will
%probably be named /dev/mmcblkX where X is some number and if the memory card
%reader is connected through \ac{USB}, then it is likely called /dev/sdX.
Make absolutely sure to write to the correct device as everything will be
overwritten!
Inserting/Ejecting the memory card a couple of times and using the commands
below may help deducing the correct device:
%The commands below may help deduce which device is the correct:
%Below is a few commands that may help you to deduce which device is correct:

>>>>

\begin{lstlisting}[]
# mount ${DEV}p2 ${ROOTDIR}
# sed -i '$a /dev/mmcblk0p3 /home ext4 defaults,noatime 0 2' ${ROOTDIR}/etc/fstab
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

If the last command was executed correctly, the
\texttt{\${ROOTDIR}/etc/fstab} file should have the new line. However,
the line will not be properly indented. To verify the correct line
insertion and fix the indentation, edit the file with
\texttt{sudo vim \$\{ROOTDIR\}/etc/fstab}. The resulting file should like
the following:

\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/etc/fstab}@>
<@\textcolor{gray}{
----------------------------------------}
\Reactivatenumber @>
proc            /proc            proc    defaults          0       0
/dev/mmcblk0p1  /boot            vfat    defaults          0       2
/dev/mmcblk0p2  /                ext4    defaults,noatime  0       1
/dev/mmcblk0p3  /home            ext4    defaults,noatime  0       2
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Originally, the home folder is located in the root filesystem. Although,
we have to move its content to the new home partition and store it properly

\begin{lstlisting}[]
# mount ${DEV}p3 ${ROOTDIR}/mnt
# mv ${ROOTDIR}/home/* ${ROOTDIR}/mnt/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

If the steps are successfully executed up to this point, the customized image
is ready to be deployed into the \ac{Raspi}s. In the following section, we
indicate how to proceed with the writing of the image into various memory
cards, although a more complex setup with a \ac{HTTP} server is also presented
in Section~\ref{sec:http} of the Appendix.

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card.
The testbed administrator needs to insert each memory card in its \ac{PC}
and follow the procedure in this section. A given card will be available as
\texttt{/dev/mmcblk*} or \texttt{/dev/sd*} with X a given

For internal memory card readers,
it will probably be named /dev/mmcblkX where X is a given integer number
and if the memory card reader is connected through \ac{USB}, then it is likely called /dev/sdX. It is very important Make absolutely sure to write to the correct device as everything will be overwritten!
Inserting/Ejecting the memory card a couple of times and using the commands
below may help deducing the correct device:
%The commands below may help deduce which device is the correct:
%Below is a few commands that may help you to deduce which device is correct:
